---
title: "Ulta Text Analysis"
author: Andrew Mashhadi
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

# Load Libraries

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(tidytext) 
library(ggplot2)
library(ggpubr)
library(tidyr)
library(stringr)
```

# Analysis

Reading in the the full dataframe of webscraped data \texttt{full\_df}.

&nbsp;&nbsp;
```{r}

## set data path
PATH_ULTA_TEXT_DIR <- Sys.getenv("ULTA_TEXT_DATA")
PATH_ULTA_PRODUCT_NAMES <-paste0(PATH_ULTA_TEXT_DIR, '/products/product_dict.csv')

## read in product names
product_names <- read.csv(PATH_ULTA_PRODUCT_NAMES)[, 2:3]

## get full paths to all data files
csv_files <- list.files(PATH_ULTA_TEXT_DIR, pattern = "csv$", full.names = T)
brand_names <- list.files(PATH_ULTA_TEXT_DIR, pattern = "csv$", full.names = F)

# initiallize df
full_df <- data.frame(matrix(ncol = 7, nrow = 0))
colnames(full_df) <- c('id', 'class', 'text', 'reviews', 
                       'rating', 'price', 'brand')

## read in product names
for (i in 1:length(csv_files)) {
  
  tmp <- read.csv(csv_files[i])[, 2:7]

  tmp <- tmp %>% 
    mutate(brand=str_replace(brand_names[i], ".csv", ""))
  
  full_df <- rbind(full_df, tmp)
  
}

# remove duplicates (sometimes same product page woudl appear a few times)
full_df <- full_df %>% 
  distinct()

full_df <- full_df %>% 
  group_by(id) %>% 
  mutate(rev_num=1:n()) %>% 
  ungroup()


# join with product names found seperately
full_df <- full_df %>% 
   inner_join(product_names %>% 
                distinct())


```
&nbsp;&nbsp;

Create dataframe for each word in each review.

&nbsp;&nbsp;
```{r}

ona_df_og <- full_df %>% 
   na.omit() %>% 
   filter(reviews != "")

tidy_revs <- ona_df_og %>% 
   unnest_tokens(word, reviews) %>% 
   filter(!grepl('[0-9]', word)) %>%
   mutate(word = str_remove_all(word, "[:punct:]")) %>%  
   anti_join(stop_words)


tidy_revs %>% 
  count(word, sort=T) %>% 
  head(n=10)

```
&nbsp;&nbsp;

We now build word cloud of words for positive reviews.

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE, fig.align='center'}

# load library
library(wordcloud)

# set seed
set.seed(1128)

tidy_revs %>% 
  filter(rating > 4.5) %>% 
  filter(!(word %in% c("hair", "product"))) %>% 
  count(word) %>% 
  with(wordcloud(word, n, max.words = 100, colors = "blue"))

```
&nbsp;&nbsp;

We now build word cloud of words for negative reviews.

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE, fig.align='center'}

# set seed
set.seed(1128)

tidy_revs %>% 
  filter(rating < 1.5) %>% 
  filter(!(word %in% c("hair", "product"))) %>% 
  count(word) %>% 
  with(wordcloud(word, n, max.words = 100, colors = "red"))


```
&nbsp;&nbsp;

Get sentiment per product. Join sentiment to main dataframe.

&nbsp;&nbsp;
```{r}

# get sentiments for each review
rev_sents <- tidy_revs %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(id, rev_num) %>% 
  summarise(sentiment = sum(value))

# treat each review equally (with weight) then get prop. positive
rev_sents <- rev_sents %>% 
  filter(sentiment != 0) %>% 
  mutate(sentiment=as.integer(sentiment > 0)) %>% 
  group_by(id) %>% 
  summarise(pos_sentiment=mean(sentiment))


# merge sentiments with reviews
ona_df <- ona_df_og %>% 
  inner_join(rev_sents, by="id") %>% 
  group_by(id) %>%
  slice(1) %>% 
  ungroup() %>% 
  select(-c(reviews, rev_num))

```
&nbsp;&nbsp;

Correlation test between sentiment scores and star ratings. Sample 100 products and demonstrate the effectiveness of the sentiment analysis with a plot.

&nbsp;&nbsp;
```{r}

# correlation test
cor.test(ona_df$rating, ona_df$pos_sentiment)


# sentiment vs star rating evaluation figure
set.seed(19)
samp_df <- slice_sample(ona_df, n = 100)

bind_rows(samp_df %>% 
            mutate(rating_type="Sentment Score", 
                   rev_rating=pos_sentiment) %>% 
            select(-c(rating, pos_sentiment, text)), 
          samp_df %>% 
            mutate(rating_type="Star Rating", 
                   rev_rating=rating) %>% 
            select(-c(rating, pos_sentiment, text))) %>%
  ggplot(aes(name, rev_rating, fill = rating_type)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~rating_type, ncol = 1, scales = "free_y") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank()) +
  xlab("Product") + 
  ylab("Rating")

```
&nbsp;&nbsp;

## Using Sentiment and Rating with Description

All description words by sentiment and rating.

&nbsp;&nbsp;
```{r, warning=FALSE}

tidy_desc <- ona_df %>% 
  filter(pos_sentiment != 0.5) %>% 
  mutate(sentiment = case_when( 
                            pos_sentiment < 0.5 ~ "negative",
                            pos_sentiment > 0.5 ~ "positive")) %>% 
  select(-c(pos_sentiment)) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)

tidy_desc %>% 
  count(sentiment, word, sort = TRUE) %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  mutate(word = reorder(word, n))
  
A <- tidy_desc %>% 
     count(sentiment, word, sort = TRUE) %>%
     ungroup() %>% 
     filter(sentiment=="negative") %>% 
     slice_max(n, n = 10) %>% 
     mutate(word = reorder(word, n)) %>%
     ggplot(aes(n, word)) +
     geom_col(show.legend = FALSE, fill="#F8766D") +
     facet_wrap(~sentiment, scales = "free_y") +
     labs(x = "Contribution to sentiment",
          y = NULL)

B <- tidy_desc %>% 
     count(sentiment, word, sort = TRUE) %>%
     ungroup() %>% 
     filter(sentiment=="positive") %>% 
     slice_max(n, n = 10) %>% 
     mutate(word = reorder(word, n)) %>%
     ggplot(aes(n, word)) +
     geom_col(show.legend = FALSE, fill="#00BFC4") +
     facet_wrap(~sentiment, scales = "free_y") +
     labs(x = "Contribution to sentiment",
          y = NULL)

f <- ggarrange(A, B,
               labels = NULL,
               ncol = 2, nrow = 1)
annotate_figure(f,
               top = text_grob("Total Description Terms", 
                               color = "Black", 
                               size = 14))


######################################################

rtidy_desc <- ona_df %>% 
  mutate(rating = case_when( 
                            rating >= 3.5 ~ "good",
                            rating < 3.5 ~  "bad")) %>% 
  select(-c(pos_sentiment)) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)

rtidy_desc %>% 
  count(rating, word, sort = TRUE) %>%
  group_by(rating) %>%
  slice_max(n, n = 10) %>% 
  mutate(word = reorder(word, n))

A <- rtidy_desc %>% 
     count(rating, word, sort = TRUE) %>%
     ungroup() %>% 
     filter(rating=="bad") %>% 
     slice_max(n, n = 10) %>% 
     mutate(word = reorder(word, n)) %>%
     ggplot(aes(n, word)) +
     geom_col(show.legend = FALSE, fill="#F8766D") +
     facet_wrap(~rating, scales = "free_y") +
     labs(x = "Contribution to sentiment",
          y = NULL)

B <- rtidy_desc %>% 
     count(rating, word, sort = TRUE) %>%
     ungroup() %>% 
     filter(rating=="good") %>% 
     slice_max(n, n = 10) %>% 
     mutate(word = reorder(word, n)) %>%
     ggplot(aes(n, word)) +
     geom_col(show.legend = FALSE, fill="#00BFC4") +
     facet_wrap(~rating, scales = "free_y") +
     labs(x = "Contribution to sentiment",
          y = NULL)

f <- ggarrange(A, B,
               labels = NULL,
               ncol = 2, nrow = 1)
annotate_figure(f,
               top = text_grob("Total Description Terms", 
                               color = "Black", 
                               size = 14))



```
&nbsp;&nbsp;

Obtain descriptive term associations with product sentiment (or rating).

&nbsp;&nbsp;
```{r}

tidy_desc %>% 
  count(sentiment, word, sort = TRUE) %>%
  ungroup() %>% 
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(positive=positive/sum(positive), negative=negative/sum(negative)) %>% 
  mutate(diff = positive-negative) %>% 
  arrange(desc(diff)) %>% 
  filter(diff!=0) %>% 
  mutate(emphasis = case_when( 
                          diff > 0 ~ "positive associated",
                          diff < 0 ~ "negative associated"), 
         diff=abs(diff)) %>% 
  group_by(emphasis) %>% 
  slice_max(diff, n=15) %>% 
  select(-c(positive, negative)) %>% 
  ungroup() %>%
  mutate(word = reorder(word, diff)) %>%
  ggplot(aes(diff, word, fill = emphasis)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~emphasis, scales = "free_y") +
  labs(x = "Description Frequency - Product Sentiment Association",
       y = NULL) +
  ggtitle("Term Association with Product Sentiment") + 
  theme(plot.title = element_text(hjust = 0.5))


######################################################


rtidy_desc %>% 
  count(rating, word, sort = TRUE) %>%
  ungroup() %>% 
  pivot_wider(names_from = rating, values_from = n, values_fill = 0) %>% 
  mutate(good=good/sum(good), bad=bad/sum(bad)) %>% 
  mutate(diff = good-bad) %>% 
  arrange(desc(diff)) %>% 
  filter(diff!=0) %>% 
  mutate(emphasis = case_when( 
                          diff > 0 ~ "positive associated",
                          diff < 0 ~ "negative associated"), 
         diff=abs(diff)) %>% 
  group_by(emphasis) %>% 
  slice_max(diff, n=15) %>% 
  select(-c(good, bad)) %>% 
  ungroup() %>%
  mutate(word = reorder(word, diff)) %>%
  ggplot(aes(diff, word, fill = emphasis)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~emphasis, scales = "free_y") +
  labs(x = "Description Frequency - Product Rating Association",
       y = NULL) +
  ggtitle("Term Association with Product Rating") + 
  theme(plot.title = element_text(hjust = 0.5))
```
&nbsp;&nbsp;

Looks like hair, scalp, eye make-up lean more negative, while face, skin, lips, and fragrance lean more positive.

Associated Wordcloud

&nbsp;&nbsp;
```{r, fig.align='center'}

set.seed(7)
library(wordcloud)
library(reshape2)


rtidy_desc  %>%
  count(word, rating, sort = TRUE) %>%
  acast(word ~ rating, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("red", "blue"),
                   max.words = 100)
  

    
```
&nbsp;&nbsp;

Best rating and sentiment brand analysis. Reporting average price of top 10.

&nbsp;&nbsp;
```{r, fig.align='center', fig.height=6, fig.width=8}

# set hyper-parameter
alpha <- 0.6

# merge sentiments with reviews, keep number of reviews first
ona_df <- ona_df_og %>% 
  inner_join(rev_sents, by="id") %>% 
  group_by(id) %>%
  slice_max(rev_num) %>% 
  ungroup() %>% 
  select(-c(reviews))

# by brand
brand_desc <- ona_df %>% 
  select(c(text, rating, price, brand, pos_sentiment, rev_num)) %>% 
  group_by(brand) %>% 
  summarise(text=paste0(text, collapse = " "), 
            rating=mean(rating), 
            price=mean(price),
            pos_sentiment=mean(pos_sentiment),
            rev_num=sum(rev_num))

# top 10 sentiment & rated brands
top10 <- brand_desc %>% 
  filter(rev_num > 25) %>% 
  select(-c(text)) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(desc(mixed_rating), rev_num) %>% 
  head(n=10)

cat("Mean price of brands with top 10 highest rating / sentiment: $", 
    mean(top10$price), "\n")
cat("Mean price of all products: $", mean(ona_df$price), "\n")

# by word
tidy_brand <- brand_desc %>% 
  filter(rev_num > 25) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(desc(mixed_rating), rev_num) %>% 
  head(n=6) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)

L <- list()
brands <- c("rituals", "montblanc", "azzaro", "skin-gym", 
            "kate-spade-new-york", "idesign")
for (i in 1:length(brands)) {
  
  L[[i]] <- tidy_brand %>% 
            count(brand, word, sort = TRUE) %>%
            bind_tf_idf(word, brand, n) %>% 
            filter(brand==brands[i]) %>% 
            filter(!(word %in% brands)) %>% 
            group_by(brand) %>%
            slice_max(tf_idf, n=6, with_ties=FALSE) %>% 
            mutate(word=reorder(word, tf_idf)) %>% 
            ggplot(aes(tf_idf, word)) +
            geom_col(show.legend = FALSE, fill="#00BFC4") +
            facet_wrap(~brand, scales = "free_y") +
            labs(x = "TF-IDF",
                 y = NULL)
}

f <- ggarrange(plotlist=L, 
               labels = NULL,
               ncol = 3, nrow = 2)

annotate_figure(f,
               top = text_grob(paste("Frequent terms in Best Rating &", 
                                     "Sentiment Brands"), 
                               color = "Black", 
                               size = 14))
    
```
&nbsp;&nbsp;

Lowest rating and sentiment brand analysis. Reporting average price of worst 10.

&nbsp;&nbsp;
```{r, fig.align='center', fig.height=6, fig.width=8}

# top 10 sentiment & rated brands
top10 <- brand_desc %>% 
  filter(rev_num > 25) %>% 
  select(-c(text)) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(mixed_rating, rev_num) %>% 
  head(n=10) 

cat("Mean price of brands with lowest 10 worst rating / sentiment: $", 
    mean(top10$price), "\n")
cat("Mean price of all products: $", mean(ona_df$price), "\n")

# by word
tidy_brand <- brand_desc %>% 
  filter(rev_num > 25) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(mixed_rating, rev_num) %>% 
  head(n=6) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)

L <- list()
brands <- c("nair", "nads-natural", "hollywood-fashion-secrets") #, 
            #"punky-colour", "pravana", "invisibobble")
for (i in 1:length(brands)) {
  
  L[[i]] <- tidy_brand %>% 
            count(brand, word, sort = TRUE) %>%
            bind_tf_idf(word, brand, n) %>% 
            filter(brand==brands[i]) %>% 
            filter(!(word %in% brands)) %>% 
            group_by(brand) %>%
            slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
            mutate(word=reorder(word, tf_idf)) %>% 
            ggplot(aes(tf_idf, word)) +
            geom_col(show.legend = FALSE, fill="#F8766D") +
            facet_wrap(~brand, scales = "free_y") +
            labs(x = "TF-IDF",
                 y = NULL)
}

f <- ggarrange(plotlist=L, 
               labels = NULL,
               ncol = 3, nrow = 1)

annotate_figure(f,
               top = text_grob(paste("Frequent terms in Worst Rated &", 
                                     "Sentiment Brands"), 
                               color = "Black", 
                               size = 14))
    
```
&nbsp;&nbsp;

Best rating and sentiment product category analysis. Reporting average price of best 10.

&nbsp;&nbsp;
```{r, fig.align='center', fig.height=6, fig.width=8}

# set hyper-parameter
alpha <- 0.6

# by product category
product_cats <- ona_df %>% 
  select(c(text, rating, price, class, pos_sentiment, rev_num)) %>% 
  group_by(class) %>% 
  summarise(text=paste0(text, collapse = " "), 
            rating=mean(rating), 
            price=mean(price),
            pos_sentiment=mean(pos_sentiment),
            rev_num=sum(rev_num))

# top 10 sentiment & rated product classes
top10 <- product_cats %>% 
  filter(rev_num > 30) %>% 
  select(-c(text)) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(desc(mixed_rating), rev_num) %>% 
  head(n=10)

cat("Mean price of product categories with top 10 highest rating / sentiment: $", 
    mean(top10$price), "\n")
cat("Mean price of all products: $", mean(ona_df$price), "\n")

# by word
tidy_product_cat <- product_cats %>% 
  filter(rev_num > 30) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(desc(mixed_rating), rev_num) %>% 
  head(n=6) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)

L <- list()
pclasses <- c("BeardCare", "Cologne", "BodyLotions", "MakeupBags&Organizers",
            "AfterSunCare", "BodyLotion")
for (i in 1:length(pclasses)) {

  L[[i]] <- tidy_product_cat %>% 
            count(class, word, sort = TRUE) %>%
            bind_tf_idf(word, class, n) %>% 
            filter(class==pclasses[i]) %>% 
            group_by(class) %>%
            slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
            mutate(word=reorder(word, tf_idf)) %>% 
            ggplot(aes(tf_idf, word)) +
            geom_col(show.legend = FALSE, fill="#00BFC4") +
            facet_wrap(~class, scales = "free_y") +
            labs(x = "TF-IDF",
                 y = NULL)
  
}

f <- ggarrange(plotlist=L, 
               labels = NULL,
               ncol = 3, nrow = 2)

annotate_figure(f,
               top = text_grob(paste("Frequent terms in Best Rating & Sentiment", 
                                      "Product Categories"), 
                               color = "Black", 
                               size = 14))
    
```
&nbsp;&nbsp;

Lowest rating and sentiment product category analysis. Reporting average price of worst 10.

&nbsp;&nbsp;
```{r, fig.align='center', fig.height=6, fig.width=8}

# set hyper-parameter
alpha <- 0.6

# top 10 sentiment & rated product classes
top10 <- product_cats %>% 
  filter(rev_num > 30) %>% 
  select(-c(text)) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(mixed_rating, rev_num) %>% 
  head(n=10)

cat("Mean price of product categories with lowest 10 worst rating / sentiment: $", 
    mean(top10$price), "\n")
cat("Mean price of all products: $", mean(ona_df$price), "\n")

# by word
tidy_product_cat <- product_cats %>% 
  filter(rev_num > 30) %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  arrange(mixed_rating, rev_num) %>% 
  head(n=6) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)

L <- list()
pclasses <- c("HairRollers", "EyeMakeupRemover", "HairRemovalTools", 
              "HairColor&Bleach", "Trend&FashionAccessories", "SelfCare&Wellness")
for (i in 1:length(pclasses)) {
  
  
  L[[i]] <- tidy_product_cat %>% 
            count(class, word, sort = TRUE) %>%
            bind_tf_idf(word, class, n) %>% 
            filter(class==pclasses[i]) %>% 
            group_by(class) %>%
            slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
            mutate(word=reorder(word, tf_idf)) %>% 
            ggplot(aes(tf_idf, word)) +
            geom_col(show.legend = FALSE, fill="#F8766D") +
            facet_wrap(~class, scales = "free_y") +
            labs(x = "TF-IDF",
                 y = NULL)
}

f <- ggarrange(plotlist=L, 
               labels = NULL,
               ncol = 3, nrow = 2)

annotate_figure(f,
               top = text_grob(paste("Frequent terms in Worst Rating &", 
                                     "Sentiment Product Categories"), 
                               color = "Black", 
                               size = 14))
    
```
&nbsp;&nbsp;

Assess best brand descriptions within specific product classes. Use categories, shampoo, face-moisturizer, and mascara.

&nbsp;&nbsp;
```{r}

product_brands <- ona_df %>% 
  filter(class=="Shampoo" | class=="FaceMoisturizer" | class=="Mascara") %>% 
  select(c(text, rating, price, class, brand, pos_sentiment, rev_num)) %>% 
  group_by(class, brand) %>% 
  summarise(text=paste0(text, collapse = " "), 
            rating=mean(rating), 
            price=mean(price),
            pos_sentiment=mean(pos_sentiment),
            rev_num=sum(rev_num)) %>% 
  ungroup()
  
# print list of top brands for each group
product_brands %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(class) %>% 
  slice_max(mixed_rating, n=4, with_ties = FALSE) %>% 
  select(class, brand) %>% 
  print(n=12)

tidy_brands <- product_brands %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(class) %>% 
  slice_max(mixed_rating, n=4, with_ties = FALSE) %>% 
  group_by(class, brand) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)
  

pclasses <- c("Shampoo", "FaceMoisturizer", "Mascara")

for (i in 1:length(pclasses)) {
  
  print(tidy_brands %>% 
    filter(class==pclasses[i]) %>% 
    count(brand, word, sort = TRUE) %>%
    bind_tf_idf(word, brand, n) %>% 
    group_by(brand) %>%
    slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
    mutate(word=reorder(word, tf_idf)) %>% 
    ggplot(aes(tf_idf, word)) +
    geom_col(show.legend = FALSE, fill="#00BFC4") +
    facet_wrap(~brand, scales = "free_y") +
    labs(x = "TF-IDF",
         y = NULL, 
         title = paste("Product Category:", pclasses[i])))
    
  
}
    
```
&nbsp;&nbsp;

Assess worst rated brand descriptions within specific product classes. Use categories, shampoo, face-moisturizer, and mascara.

&nbsp;&nbsp;
```{r}
  
# print list of top brands for each group
product_brands %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(class) %>% 
  slice_min(mixed_rating, n=4, with_ties = FALSE) %>% 
  select(class, brand, mixed_rating) %>% 
  print(n=12)

tidy_brands <- product_brands %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(class) %>% 
  slice_min(mixed_rating, n=4, with_ties = FALSE) %>% 
  group_by(class, brand) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)
  

pclasses <- c("Shampoo", "FaceMoisturizer", "Mascara")

for (i in 1:length(pclasses)) {
  
  print(tidy_brands %>% 
    filter(class==pclasses[i]) %>% 
    count(brand, word, sort = TRUE) %>%
    bind_tf_idf(word, brand, n) %>% 
    group_by(brand) %>%
    slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
    mutate(word=reorder(word, tf_idf)) %>% 
    ggplot(aes(tf_idf, word)) +
    geom_col(show.legend = FALSE, fill="#F8766D") +
    facet_wrap(~brand, scales = "free_y") +
    labs(x = "TF-IDF",
         y = NULL, 
         title = paste("Product Category:", pclasses[i])))
    
  
}
    
```
&nbsp;&nbsp;


Assess best product class descriptions within specific brand. Using brands peach-lily and colourpop.

&nbsp;&nbsp;
```{r}

product_cats <- ona_df %>% 
  filter(brand =="peach-lily" | brand == "colourpop") %>% 
  select(c(text, rating, price, class, brand, pos_sentiment, rev_num)) %>% 
  group_by(brand, class) %>% 
  summarise(text=paste0(text, collapse = " "), 
            rating=mean(rating), 
            price=mean(price),
            pos_sentiment=mean(pos_sentiment),
            rev_num=sum(rev_num)) %>% 
  ungroup()
  
# print list of top cats for each brand
product_cats %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(brand) %>% 
  slice_max(mixed_rating, n=4, with_ties = FALSE) %>% 
  select(class, brand) %>% 
  print(n=8)

tidy_cats <- product_cats %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(brand) %>% 
  slice_max(mixed_rating, n=4, with_ties = FALSE) %>% 
  group_by(class, brand) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)
  
brands <- c("peach-lily", "colourpop")

for (i in 1:length(brands)) {
  
  print(tidy_cats %>% 
    filter(brand==brands[i]) %>% 
    count(class, word, sort = TRUE) %>%
    bind_tf_idf(word, class, n) %>% 
    group_by(class) %>%
    slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
    mutate(word=reorder_within(word, tf_idf, class)) %>% 
    ggplot(aes(tf_idf, word)) +
    geom_col(show.legend = FALSE, fill="#00BFC4") +
    facet_wrap(~class, scales = "free_y") +
    scale_y_reordered() +
    labs(x = "TF-IDF",
         y = NULL, 
         title = paste("Brand:", brands[i])))
    
  
}
    
    
```
&nbsp;&nbsp;

Assess worst rated brand descriptions within specific product classes. Using brands peach-lily and colourpop.

&nbsp;&nbsp;
```{r}

# print list of top cats for each brand
product_cats %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(brand) %>% 
  slice_min(mixed_rating, n=4, with_ties = FALSE) %>% 
  select(class, brand) %>% 
  print(n=8)

tidy_cats <- product_cats %>% 
  mutate(mixed_rating=alpha*pos_sentiment+(1-alpha)*(rating/5)) %>% 
  group_by(brand) %>% 
  slice_min(mixed_rating, n=4, with_ties = FALSE) %>% 
  group_by(class, brand) %>% 
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)
  
brands <- c("peach-lily", "colourpop")

for (i in 1:length(brands)) {
  
  print(tidy_cats %>% 
    filter(brand==brands[i]) %>% 
    count(class, word, sort = TRUE) %>%
    bind_tf_idf(word, class, n) %>% 
    group_by(class) %>%
    slice_max(tf_idf, n=10, with_ties=FALSE) %>% 
    mutate(word=reorder_within(word, tf_idf, class)) %>% 
    ggplot(aes(tf_idf, word)) +
    geom_col(show.legend = FALSE, fill="#F8766D") +
    facet_wrap(~class, scales = "free_y") +
    scale_y_reordered() +
    labs(x = "TF-IDF",
         y = NULL, 
         title = paste("Brand:", brands[i])))
    
  
}
    
    
```
&nbsp;&nbsp;

## Topic Modeling

Create corpus.

&nbsp;&nbsp;
```{r}

library(tm)

brands_df <- ona_df %>% 
  select(c(text, rating, price, class, brand, pos_sentiment, rev_num)) %>% 
  group_by(brand) %>% 
  summarise(text=paste0(text, collapse = " "), 
            rating=mean(rating), 
            price=mean(price),
            pos_sentiment=mean(pos_sentiment),
            rev_num=sum(rev_num)) %>% 
  ungroup()

# tidy desc data by brand
tidy_brands <- brands_df %>%
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words)
  

# cast tidy data into dtm
dtm <- tidy_brands %>%
  count(brand, word, sort=TRUE) %>%
  cast_dtm(brand, word, n)

# inspect dtm
dtm %>% inspect()
    
    
```
&nbsp;&nbsp;

Build topic models.

&nbsp;&nbsp;
```{r}

library(topicmodels)
options(scipen=2)

brands_lda <- LDA(dtm, k = 3, control = list(seed = 1234))
brands_lda
    
    
```
&nbsp;&nbsp;

Terms that are most common within each topic.

&nbsp;&nbsp;
```{r}

brands_topics <- tidy(brands_lda, matrix = "beta")

brands_top_terms <- brands_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

brands_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered() + 
  ggtitle("Most Common Words In Each Topic")
    
```
&nbsp;&nbsp;

Topic 3 appears to be hair related, topic 2 looks like facial and body cleansers/moisturizers, and topic 1 looks like makeup and lashes.

Now we look at the each brands probability of being in each topic.

&nbsp;&nbsp;
```{r}

brand_documents <- tidy(brands_lda, matrix = "gamma")
brand_documents

brand_documents %>%
  group_by(topic) %>%
  slice_max(gamma, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -gamma) %>% 
  select(c(document, topic)) %>% 
  print(n=30)

```
&nbsp;&nbsp;

Brands sufficiently match topics as described above.

&nbsp;

Price differences, ratings, and sentiment between clusters.

&nbsp;&nbsp;
```{r}

brand_topics <- brand_documents %>% 
  group_by(document) %>% 
  slice_max(gamma) %>% 
  mutate(brand=document) %>% 
  select(-c(document, gamma))

brands_df <- brands_df %>% 
  left_join(brand_topics)

brands_df %>% 
  group_by(topic) %>% 
  summarise(Topic.Price = mean(price),
            Topic.Rating = mean(rating),
            Topic.Sentiment = mean(pos_sentiment))


```
&nbsp;&nbsp;

Nothing substantially different. 

## Correlation Plots

Using the clusters 2 and 3, plots.

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}

library(scales)


# tidy desc data by brand
tidy_brands <- brands_df %>%
  unnest_tokens(word, text) %>% 
  filter(!grepl('[0-9]', word)) %>%
  mutate(word = str_remove_all(word, "[:punct:]")) %>%  
  anti_join(stop_words) %>% 
  mutate(topic = paste0("topic", topic))

frequency <- tidy_brands %>%
  count(topic, word) %>%
  group_by(topic) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = topic, values_from = proportion) %>% 
  pivot_longer(topic2:topic3,
               names_to = "topic", values_to = "proportion")

# expect a warning about rows with missing values being removed
ggplot(frequency, aes(x = proportion, y = topic1, 
                      color = abs(topic1 - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  facet_wrap(~topic, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "topic1", x = NULL)

```
&nbsp;&nbsp;

Using the clusters 2 and 3, estimates.

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE}

# t3 vs t1
cor.test(data = frequency[frequency$topic == "topic3",],
         ~ proportion + topic1)

# t2 vs t1
cor.test(data = frequency[frequency$topic == "topic2",],
         ~ proportion + topic1)

# t2 vs t3
cor.test(frequency$proportion[frequency$topic == "topic2"], 
         frequency$proportion[frequency$topic == "topic3"])

```
&nbsp;&nbsp;


Using two different brands, plots.

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4}


frequency <- tidy_brands %>%
  filter(brand=="loreal" | brand=="colourpop" | brand=="maybelline") %>% 
  count(brand, word) %>%
  group_by(brand) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = brand, values_from = proportion) %>% 
  pivot_longer(c(`colourpop`, `maybelline`),
               names_to = "brand", values_to = "proportion")

# expect a warning about rows with missing values being removed
ggplot(frequency, aes(x = proportion, y = loreal, 
                      color = abs(loreal - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  facet_wrap(~brand, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "loreal", x = NULL)

```
&nbsp;&nbsp;

Using the brands, estimates.

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE}

# loreal vs maybelline
cor.test(data = frequency[frequency$brand == "maybelline",],
         ~ proportion + loreal)

# loreal vs colourpop
cor.test(data = frequency[frequency$brand == "colourpop",],
         ~ proportion + loreal)

# loreal vs colourpop
cor.test(frequency$proportion[frequency$brand == "colourpop"], 
         frequency$proportion[frequency$brand == "maybelline"])


```
&nbsp;&nbsp;

What else makes colourpop different from the other two? 

&nbsp;&nbsp;
```{r, warning=FALSE, message=FALSE}

l_vs_c <- tidy_brands %>%
  filter(!word %in% c("loréal", "loreal", "loreals")) %>% 
  filter(brand=="loreal" | brand=="colourpop") %>% 
  count(brand, word) %>%
  group_by(brand) %>% 
  pivot_wider(names_from = brand, values_from = n, values_fill = 0) %>% 
  mutate_if(is.numeric, list(~(. + 1) / (sum(.) + 1))) %>%
  mutate(logratio = log(loreal / colourpop)) %>%
  arrange(desc(logratio)) 

l_vs_c %>%
  group_by(logratio < 0) %>%
  slice_max(abs(logratio), n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("log odds ratio (loreal/colourpop)") +
  scale_fill_discrete(name = "", labels = c("loreal", "colourpop")) + 
  ggtitle("Term Frequencies with the Largest Differences")

l_vs_m <- tidy_brands %>%
  filter(!word %in% c("loréal", "maybelline", "maybellines")) %>% 
  filter(brand=="loreal" | brand=="maybelline") %>% 
  count(brand, word) %>%
  group_by(brand) %>% 
  pivot_wider(names_from = brand, values_from = n, values_fill = 0) %>% 
  mutate_if(is.numeric, list(~(. + 1) / (sum(.) + 1))) %>%
  mutate(logratio = log(loreal / `maybelline`)) %>%
  arrange(desc(logratio))

l_vs_m %>%
  group_by(logratio < 0) %>%
  slice_max(abs(logratio), n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("log odds ratio (loreal/maybelline)") +
  scale_fill_discrete(name = "", labels = c("loreal", "maybelline")) + 
  ggtitle("Term Frequencies with the Largest Differences")

c_vs_m <- tidy_brands %>%
  filter(!word %in% c("maybelline", "maybellines", "colourpops")) %>% 
  filter(brand=="colourpop" | brand=="maybelline") %>% 
  count(brand, word) %>%
  group_by(brand) %>% 
  pivot_wider(names_from = brand, values_from = n, values_fill = 0) %>% 
  mutate_if(is.numeric, list(~(. + 1) / (sum(.) + 1))) %>%
  mutate(logratio = log(colourpop / maybelline)) %>%
  arrange(desc(logratio)) 

c_vs_m %>%
  group_by(logratio < 0) %>%
  slice_max(abs(logratio), n = 15) %>% 
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("log odds ratio (colourpop / maybelline)") +
  scale_fill_discrete(name = "", labels = c("colourpop", "maybelline")) + 
  ggtitle("Term Frequencies with the Largest Differences")

```
&nbsp;&nbsp;

Colourpop is a bit more Gen. Z (hip, colorful, cool) while maybelline and loreal are a bit more millennials.

